maze-dataset

### 2025-03-30 docs/paper/paper.tex
wip

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={maze-dataset},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Rusheb Shah, Brandon Knutson, , Cecilia Diniz Behn, Samy Wu
Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Rusheb Shah, Brandon Knutson, , Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\author[1%
%
\ensuremath\mathparagraph]{Michael Igorevich Ivanitskiy%
  \,\orcidlink{0000-0002-4213-4993}\,%
}
\author[%
%
]{Aaron Sandoval%
  \,\orcidlink{0009-0002-8380-6140}\,%
}
\author[2%
%
]{Alex F. Spies%
  \,\orcidlink{0000-0002-8708-1530}\,%
}
\author[%
%
]{Rusheb Shah%
  \,\orcidlink{0009-0008-3058-0217}\,%
}
\author[%
%
]{Brandon Knutson%
}
\author[1%
%
]{%
  \,\orcidlink{0009-0004-8413-0239}\,%
}
\author[1%
%
]{Cecilia Diniz Behn%
  \,\orcidlink{0000-0002-8078-5105}\,%
}
\author[1%
%
]{Samy Wu Fung%
  \,\orcidlink{0000-0002-2926-4582}\,%
}

@@

\leavevmode\vadjust pre{\hypertarget{ref-chen2024iaimperative}{}}%
Chen, X., Yang, F., \& Wang, C. (2024). iA \(\^{}*\): Imperative
learning-based a \(\^{}*\) search for pathfinding. \emph{arXiv Preprint
arXiv:2403.15870}.

>>>>

\documentclass[10pt,a4paper,onecolumn]{article}
\usepackage{marginnote}
\usepackage{graphicx}
\usepackage[rgb,svgnames]{xcolor}
\usepackage{authblk,etoolbox}
\usepackage{titlesec}
\usepackage{calc}
\usepackage{tikz}
\usepackage[pdfa]{hyperref}
\usepackage{hyperxmp}
\hypersetup{%
    unicode=true,
    pdfapart=3,
    pdfaconformance=B,
    pdftitle={maze-dataset},
    pdfauthor={Michael Igorevich Ivanitskiy, Aaron Sandoval, Alex F.
Spies, Rusheb Shah, Brandon Knutson, Cecilia Diniz Behn, Samy Wu Fung},
    pdfpublication={Journal of Open Source Software},
    pdfpublisher={Open Journals},
    pdfissn={2475-9066},
    pdfpubtype={journal},
    pdfvolumenum={},
    pdfissuenum={},
    pdfdoi={N/A},
    pdfcopyright={Copyright (c) 1970, Michael Igorevich Ivanitskiy,
Aaron Sandoval, Alex F. Spies, Rusheb Shah, Brandon Knutson, Cecilia
Diniz Behn, Samy Wu Fung},
    pdflicenseurl={http://creativecommons.org/licenses/by/4.0/},
    colorlinks=true,
    linkcolor=[rgb]{0.0, 0.5, 1.0},
    citecolor=Blue,
    urlcolor=[rgb]{0.0, 0.5, 1.0},
    breaklinks=true
}
% https://tex.stackexchange.com/a/535849
% Create an OutputIntent in order to correctly specify colours
\immediate\pdfobj stream attr{/N 3} file{sRGB.icc}
\pdfcatalog{%
  /OutputIntents [
    <<
      /Type /OutputIntent
      /S /GTS_PDFA1
      /DestOutputProfile \the\pdflastobj\space 0 R
      /OutputConditionIdentifier (sRGB)
      /Info (sRGB)
    >>
  ]
}
\pdfvariable omitcidset=1
\usepackage{caption}
\usepackage{orcidlink}
\usepackage{tcolorbox}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{seqsplit}
\usepackage{xstring}

@@

\author[1%
%
\ensuremath\mathparagraph]{Michael Igorevich Ivanitskiy%
  \,\orcidlink{0000-0002-4213-4993}\,%
}
\author[%
%
]{Aaron Sandoval%
  \,\orcidlink{0009-0002-8380-6140}\,%
}
\author[2%
%
]{Alex F. Spies%
  \,\orcidlink{0000-0002-8708-1530}\,%
}
\author[%
%
]{Rusheb Shah%
  \,\orcidlink{0009-0008-3058-0217}\,%
}
\author[1%
%
]{Brandon Knutson%
  \,\orcidlink{0009-0004-8413-0239}\,%
}
\author[1%
%
]{Cecilia Diniz Behn%
  \,\orcidlink{0000-0002-8078-5105}\,%
}
\author[1%
%
]{Samy Wu Fung%
  \,\orcidlink{0000-0002-2926-4582}\,%
}

@@

\leavevmode\vadjust pre{\hypertarget{ref-chen2024iaimperative}{}}%
Chen, X., Yang, F., \& Wang, C. (2024). {iA*}: Imperative learning-based
{A*} search for pathfinding. \emph{arXiv Preprint arXiv:2403.15870}.
